\documentclass[12pt]{article}

% ── packages ──────────────────────────────────────────────────────────────────
\usepackage{amsmath,amssymb,amsthm}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{enumitem}

\usepackage{parskip}

\geometry{letterpaper, margin=1in}

% ── theorem environments ───────────────────────────────────────────────────────
\newtheorem{theorem}{Theorem}[section]
\newtheorem{definition}[theorem]{Definition}
\newtheorem{postulate}[theorem]{Postulate}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{remark}[theorem]{Remark}

% ── title block ───────────────────────────────────────────────────────────────
\title{\textbf{The Absolute Moment Postulate: Necessity, Consistency,\\
and the PCD Cycle in Conscious Point Physics}\\[6pt]
{\large Companion Paper to ``Mechanistic Derivation of Relativistic Effects\\
via Space Stress Vector (SSV) in the Dipole Sea'' (Version~16)}}

\author{Thomas Lee Abshier, ND\\
Hyperphysics Institute\\
\texttt{https://hyperphysics.com}\\
\texttt{drthomas007@protonmail.com}}

\date{12 March 2026 --- Version~3}

\begin{document}
\maketitle

% ── keywords ──────────────────────────────────────────────────────────────────
\noindent\textbf{Keywords:} Conscious Point Physics, Absolute Moment postulate,
DI-bit conservation, atemporal Nexus, 600-cell lattice, PCD cycle,
Grid Point broadcast, inverse-square SSV falloff, stress-invariant timelike
advance, quantum tunnelling, left-handed chirality.

% ── abstract ──────────────────────────────────────────────────────────────────
\begin{abstract}
The Absolute Moment postulate of Conscious Point Physics (CPP) asserts that
every Conscious Point (CP) advances exactly $l_P$ in the timelike direction
once per universal tick $t_P = l_P/c$, frame-independently and independent of
local Voronoi-cell stress.  We establish three results.  First, the postulate
is \emph{necessary}: global DI-bit conservation, in which each DI-bit carries a
complete four-component address-time vector
$(\mathbf{x},\, t_{\rm abs})$, requires simultaneous ledger reconciliation
across cell boundaries; the Perceive-Compute-Displace (PCD) cycle shows that
no local, asynchronous tick can satisfy this requirement.  Second, the postulate
is \emph{consistent} with the atemporal Nexus: because the Nexus lies outside
every Voronoi cell, the timelike component $l_P$ is stress-invariant, supplying
the fixed denominator in $\text{PSR}_{\rm eff} = l_P/(1+k\cdot\Delta\text{SSV})$.
Third, the postulate is \emph{consistent} with causal field propagation: the
Grid Point SSV quantum propagates outward at one PSR shell per Moment,
distributing a fixed total SSV over a growing spherical surface and thereby
reproducing the inverse-square falloff required by Coulomb's law and
Newtonian gravity.  The PSR (communication radius, set by absolute SSV) and
the displacement step (set by net SSV) are identified as two distinct
quantities, with their coincidence for photons recovering the null-geodesic
condition.  No new postulates beyond those of Version~16 are introduced;
chirality and quantum-tunnelling phenomenology are noted as topics for
dedicated companion papers.
\end{abstract}

% ══════════════════════════════════════════════════════════════════════════════
\section{Introduction}
\label{sec:intro}
% ══════════════════════════════════════════════════════════════════════════════

The main paper (Version~16) derives time dilation, length contraction, and the
twin paradox resolution from the single geometric relation
\begin{equation}
  \text{PSR}_{\rm eff} \;=\; \frac{l_P}{1 + k\cdot\Delta\text{SSV}},
  \label{eq:PSR}
\end{equation}
where $k = l_P^3/E_P \approx 2.16\times10^{-114}$~m$^3$/J, and the timelike
advance per tick is taken to be the fixed Planck length $l_P$.  That fixed
advance is the Absolute Moment postulate.

This companion paper examines the foundational status of the postulate.
Section~\ref{sec:entities} defines the primitive entities of CPP (CPs, Grid
Points, the DI-bit string, and the Nexus) and introduces two quantities that
must be carefully distinguished: the \emph{PSR} (communication radius) and
the \emph{displacement step}.  Section~\ref{sec:pcd} introduces the
\textbf{PCD cycle} --- the Perceive $\to$ Compute $\to$ Displace operational
definition of GP and CP behaviour --- which forms the mechanical backbone of
the necessity argument.  Section~\ref{sec:necessity} uses the PCD cycle to
show that global DI-bit conservation \emph{requires} a universal tick.
Section~\ref{sec:nexus} establishes stress-invariance via the atemporality of
the Nexus.  Section~\ref{sec:4d} resolves the 4D step-budget, identifies the
PSR shell-propagation mechanism, and derives the inverse-square SSV falloff.
Section~\ref{sec:sr} confirms consistency with the SR derivation of
Version~16.  Section~\ref{sec:conclusion} concludes.

\begin{remark}[Axiomatic status]
The Absolute Moment is retained as an \emph{axiomatic postulate}, not derived
from deeper primitives.  The strategy mirrors that of Version~16 for the
600-cell: one assumes the postulate, derives its consequences, and validates it
by the coherence and empirical accuracy of those consequences.  ``Necessity''
in Section~\ref{sec:necessity} means that, given the other CPP postulates,
\emph{no self-consistent alternative} to a universal tick exists --- which
is the strongest achievable justification for an axiomatic entity.
\end{remark}

% ══════════════════════════════════════════════════════════════════════════════
\section{Primitive Entities and Definitions}
\label{sec:entities}
% ══════════════════════════════════════════════════════════════════════════════

\begin{definition}[Conscious Point (CP)]
A CP is an irreducible, conscious, mobile entity carrying a DI-bit string.
It has polarity ($\pm 1$), type (electron-type or quark-type), and resides at
exactly one Grid Point at any given tick.  CPs do not broadcast; they move.
\end{definition}

\begin{definition}[Grid Point (GP)]
A GP is a static, conscious address in the 600-cell lattice.  It serves a
\emph{dual role}: (i)~as a \emph{spatial address}, providing a unique
$(x,y,z,t_{\rm abs})$ label for each tick, and (ii)~as a \emph{conduit},
receiving SSV contributions from all GPs whose PSR contains it, summing those
contributions, and broadcasting the resulting field to all GPs within its own
PSR.  The CP currently resident on a GP acquires the GP's address-time stamp
for all DI-bit strings emitted during that Moment.
\end{definition}

\begin{definition}[DI-bit String]
The complete state vector carried by each CP is
\begin{equation}
  \text{DI-bit} \;=\;
  \bigl\{\,\text{identity},\; \pm1\ (\text{polarity}),\;
  \text{type},\; (x,y,z,t_{\rm abs})\ (\text{address-time})\,\bigr\},
  \label{eq:dibit}
\end{equation}
where $t_{\rm abs}$ is the absolute tick counter at emission.  The SSV
contribution of a CP is \emph{implicit in its type} (electron-type carries
one characteristic SSV quantum; quark-type carries another); it is
\emph{not} an independent variable field in the DI-bit string.  The
four-component address-time vector $(x,y,z,t_{\rm abs})$ serves as a
unique identifier for every emitted signal, enabling each GP's register
to enforce the no-double-counting rule (Section~\ref{sec:4d}) without
circularity.
\end{definition}

\begin{remark}[Absolute time as axiomatic postulate]
The component $t_{\rm abs}$ is a \emph{primitive postulate}, not derived from
the Absolute Moment.  Its necessity is evidenced by internal consistency: it
prevents positive-feedback saturation of the SSV field
(Section~\ref{sec:4d}), provides an eternally decodable record of the
universe's history, and suggests mechanisms for quantum entanglement and
memory that will be explored in dedicated companion papers.  The relationship
between $t_{\rm abs}$ and the Absolute Moment tick is the same as the
relationship between a clock face and the mechanism that drives it: the tick
mechanism (derived in Section~\ref{sec:necessity}) increments the counter
whose existence is separately postulated.
\end{remark}

\begin{definition}[Atemporal Nexus]
The Nexus is the entity outside spacetime that enforces global DI-bit
conservation.  It is not a causal signal (it has no finite propagation speed);
it is a \emph{global constraint}.  Its operation is the universal tick that
synchronises the PCD cycle across all GPs and CPs simultaneously.
\end{definition}

\begin{definition}[PSR and Displacement Step --- two distinct quantities]
\label{def:psr-disp}
Two length scales govern CP motion each tick.
\begin{enumerate}[label=(\roman*)]
  \item The \textbf{Planck Sphere Radius (PSR)} is the communication radius
    of a GP: the radius of the sphere within which the GP broadcasts its SSV
    quantum each Moment.  The PSR is determined by the \emph{absolute} SSV
    magnitude (the scalar sum of all SSV contributions present at the GP):
    \begin{equation}
      \text{PSR} \;=\; \frac{l_P}{1 + k\cdot|\text{SSV}|_{\rm abs}}.
      \label{eq:PSR-def}
    \end{equation}
  \item The \textbf{displacement step} $d$ is the distance the CP moves from
    its current GP to its destination GP in the Displace phase.  It is
    determined by the \emph{net} SSV (the vector sum, including direction):
    \begin{equation}
      \mathbf{d} \;=\; d(\text{SSV}_{\rm net})\,\hat{\mathbf{n}}_{\rm net}.
      \label{eq:disp}
    \end{equation}
\end{enumerate}
For a massless CP (photon), $d = \text{PSR}$ and the two coincide, recovering
the null-geodesic condition.  For all massive CPs, $d < \text{PSR}$.  As a
special case, soliton superposition can produce an instantaneous net SSV
exceeding the PSR, giving $d > \text{PSR}$ --- the CPP mechanism for quantum
tunnelling (deferred to a dedicated companion paper).
\end{definition}

% ══════════════════════════════════════════════════════════════════════════════
\section{The PCD Cycle}
\label{sec:pcd}
% ══════════════════════════════════════════════════════════════════════════════

\begin{definition}[PCD Cycle]
\label{def:pcd}
At each Absolute Moment tick, every GP executes the following three-phase
cycle, triggered simultaneously across the entire lattice by the Nexus:

\begin{enumerate}[label=\textbf{\Alph*.}]
  \item \textbf{Perceive.}  The GP passively receives SSV contributions from
    all GPs that have it within their PSR.  Each arriving signal carries the
    sender's four-component address-time vector
    $(x_{\rm src},y_{\rm src},z_{\rm src},t_{\rm abs})$.  The GP updates its
    register, subject to the no-double-counting rule
    (Section~\ref{sec:4d}).

  \item \textbf{Compute.}  The GP calculates:
    \begin{enumerate}[label=(\roman*)]
      \item its absolute SSV magnitude $|\text{SSV}|_{\rm abs}$ from the
        register sum, and hence its own PSR via Eq.~\eqref{eq:PSR-def};
      \item the net SSV vector $\text{SSV}_{\rm net}$ (vector sum over all
        received contributions), which determines the direction and magnitude
        of the resident CP's displacement step via Eq.~\eqref{eq:disp}.
    \end{enumerate}

  \item \textbf{Displace.}  The CP resident on this GP moves to its
    destination GP, selected along the edge of the appropriately-scaled
    600-cell that most closely aligns with $\hat{\mathbf{n}}_{\rm net}$.
    Simultaneously, the GP broadcasts its own SSV quantum outward at speed
    $c$ (one PSR shell per Moment; see Section~\ref{sec:4d}).
\end{enumerate}
\end{definition}

\begin{remark}[Historical note]
The PCD cycle is the operational core of CPP, first conceived by the author
in the late 1980s and refined continuously since.  The designation
``PCD'' was introduced in the present work.
\end{remark}

The PCD cycle makes the global synchronisation requirement explicit and
mechanical: the Displace phase of tick $n$ requires that the destination GP
has completed its Perceive phase at tick $n$.  This cross-cell dependency is
the subject of Section~\ref{sec:necessity}.

% ══════════════════════════════════════════════════════════════════════════════
\section{Necessity of the Absolute Moment}
\label{sec:necessity}
% ══════════════════════════════════════════════════════════════════════════════

\begin{theorem}[Necessity of a universal tick]
\label{thm:necessity}
Given (i) the complete DI-bit state vector~\eqref{eq:dibit}, (ii) global
conservation of DI-bits, and (iii) the PCD cycle, no locally asynchronous
tick schedule is self-consistent.  A universal, simultaneous tick is the
unique schedule compatible with DI-bit conservation.
\end{theorem}

\begin{proof}
Suppose, for contradiction, that ticks are local and asynchronous: GP
$C_i$ executes its Displace phase at local time $\tau_i$, and its destination
GP $C_j$ executes its Perceive phase at local time $\tau_j \ne \tau_i$.

The DI-bit emitted by the CP on $C_i$ carries the address-time vector
$(x_i, y_i, z_i, t_{\rm abs,\,i})$.  Global conservation requires this
DI-bit to be exactly accounted for in $C_j$'s register.  But $C_j$'s
register is only updated during its Perceive phase.  If $\tau_j > \tau_i$,
the DI-bit is ``in flight'' --- its identity component is unaccounted for
during the interval $(\tau_i, \tau_j)$, violating conservation.  If
$\tau_j < \tau_i$, $C_j$'s register closes before the DI-bit departs, so
the arriving DI-bit has no open register to enter, again violating
conservation.

The only schedule that avoids both violations is $\tau_i = \tau_j$ for all
pairs $(i, j)$ related by a Displace event --- i.e., a universal, simultaneous
tick.  The unique timescale constructible from the Planck constants already
fixed in Version~16 is $t_P = l_P/c$, so the tick interval is exactly $t_P$.
\end{proof}

\begin{corollary}
The Absolute Moment postulate is the unique synchronisation schedule
consistent with global DI-bit conservation under the PCD cycle.  It is
therefore not merely consistent with the other CPP postulates; it is
necessitated by them.
\end{corollary}

% ══════════════════════════════════════════════════════════════════════════════
\section{The Atemporal Nexus and Stress-Invariance}
\label{sec:nexus}
% ══════════════════════════════════════════════════════════════════════════════

The Nexus lies outside spacetime and enforces the simultaneous global tick
without finite propagation delay.  Two consequences follow directly.

\textbf{Stress-invariance.}  The timelike advance $l_P$ is the orthogonal
$\tau$-component in the 4D Voronoi coordinate (Version~16, \S A.4).  Because
the Nexus is unaffected by local Voronoi-cell stress --- it is outside every
such cell --- $\Delta\tau = l_P/c = t_P$ for every CP, stressed or unstressed.
This is precisely the stress-invariant timelike denominator that drives
$\text{PSR}_{\rm eff}$ in Eq.~\eqref{eq:PSR}: spatial steps shorten under
stress; timelike steps do not.

\textbf{No computational bottleneck.}  The Nexus enforces conservation as a
global constraint, not as a causal signal.  Its atemporal nature means there
is no bandwidth or latency limit; the tick is a constraint, not a message.
Local PCD-cycle processing at each GP handles the SSV bookkeeping; the Nexus
supplies only the synchronisation pulse.

% ══════════════════════════════════════════════════════════════════════════════
\section{The 4D Step Budget, Shell Propagation, and Inverse-Square Falloff}
\label{sec:4d}
% ══════════════════════════════════════════════════════════════════════════════

\subsection{The 4D Step Budget}

The universe in CPP is fundamentally \emph{three spatial dimensions plus
absolute time as an address}.  It is not a four-dimensional Riemannian
manifold; the fourth component is the tick counter $t_{\rm abs}$.
Nevertheless, the constraint imposed by the Absolute Moment postulate is
Pythagorean in form.  The total ``budget'' per tick is $l_P$, partitioned as:
\begin{equation}
  l_P^2 \;=\; (c\,\Delta\tau)^2 + |\mathbf{d}_{\rm spatial}|^2,
  \label{eq:budget}
\end{equation}
where $\Delta\tau$ is the timelike advance and $\mathbf{d}_{\rm spatial}$ is
the 3D displacement.  Three limiting cases confirm consistency with
Version~16 and with standard SR:

\begin{center}
\begin{tabular}{@{}lll@{}}
\toprule
Case & $\Delta\tau$ & $|\mathbf{d}_{\rm spatial}|$ \\
\midrule
CP at rest & $l_P/c = t_P$ & $0$ \\
Photon (massless, null geodesic) & $0$ & $l_P$ \\
Massive CP at speed $v < c$ &
  $l_P\sqrt{1-v^2/c^2}$ & $l_P\,v/c$ \\
\bottomrule
\end{tabular}
\end{center}

The massive-CP case recovers the relativistic Pythagorean relation and
produces time dilation automatically: a CP moving at speed $v$ advances only
$l_P\sqrt{1-v^2/c^2}$ in the timelike direction per tick, so its proper-time
clock runs slow by exactly the Lorentz factor $\gamma$, consistent with
Version~16, \S A.4.

The photon case deserves physical elaboration.  A photon in CPP is not a
moving CP in the usual sense; it is a propagating packet of
\emph{ordered net-SSV instructions} --- a volume of GPs that have been
coherently polarised to re-broadcast in the same direction.  The photon
``moves'' because the coherent polarisation front advances at $c$ (one shell
per Moment) while individual CPs oscillate in place.  The null-geodesic
condition $\Delta\tau = 0$ reflects the fact that the polarisation front
carries no timelike budget of its own.

\subsection{GP Shell Propagation and the Inverse-Square Law}

At each Moment, a GP broadcasts its SSV quantum outward at speed $c$.
Specifically, during the Displace phase of tick $n$, the GP emits its SSV
quantum to all GPs on the spherical shell at radius $\text{PSR}$ from the
source.  This shell advances by one PSR per tick, so the wavefront reaches
a GP at distance $r$ after $r/\text{PSR}$ ticks --- causal propagation at
$c$ with no additional postulate.

The fixed total SSV quantum $Q$ is distributed over the $N(r)$ GPs on the
shell at radius $r$.  In three dimensions the shell surface area scales as
$4\pi r^2$, so the GP density on the shell is approximately constant (the
lattice is isotropic at scales large compared to $l_P$), giving:
\begin{equation}
  \text{SSV received per GP at distance }r
  \;\propto\; \frac{Q}{4\pi r^2}
  \;\propto\; \frac{1}{r^2}.
  \label{eq:invsq}
\end{equation}
This is the standard inverse-square falloff.  Coulomb's law and Newtonian
gravity therefore emerge from the shell-propagation geometry without
additional assumptions, provided $Q$ is identified with the characteristic
SSV quantum of the source CP's type.

\begin{remark}[Volume vs.\ surface]
One might consider broadcasting to all GPs within the PSR \emph{volume}
rather than the surface shell.  A fixed total $Q$ divided among
$\tfrac{4}{3}\pi r^3$ GPs would give a $1/r^3$ falloff --- inconsistent
with Coulomb's law.  Shell propagation at speed $c$ is therefore the unique
broadcast geometry that simultaneously (i)~preserves causality, (ii)~gives
$1/r^2$ falloff, and (iii)~leaves mechanisms open for super-PSR phenomena
(tunnelling, entanglement) via soliton SSV superposition
(Definition~\ref{def:psr-disp}).
\end{remark}

\subsection{The No-Double-Counting Rule}

A GP's register sums SSV contributions from all incoming signals.  Without a
damping rule, each GP would re-broadcast contributions it received, which
would re-broadcast them again, producing unbounded positive feedback and SSV
saturation.  The rule is:

\begin{postulate}[No-double-counting]
Each GP's register accepts a contribution from a given source address-time
pair $(x_{\rm src},\, t_{\rm abs})$ at most \emph{once} per tick.  Signals
with the same address-time pair arriving via different re-broadcast paths are
identified and counted only once.
\end{postulate}

The four-component address-time vector in each DI-bit~\eqref{eq:dibit}
provides the unique identifier required by this rule.  The rule is local
(each GP maintains its own register) and imposes no global bookkeeping beyond
what the PCD Perceive phase already performs.

% ══════════════════════════════════════════════════════════════════════════════
\section{Consistency with Special Relativity}
\label{sec:sr}
% ══════════════════════════════════════════════════════════════════════════════

With the Absolute Moment postulate, the 4D Voronoi insphere radius contracts
only in the three spatial directions under stress, while the timelike
component is pinned at $l_P$.  The effective 3D radius is therefore
\begin{equation}
  r_{\rm eff}^{3D}
  \;=\; \sqrt{\!\left(\frac{R_{4D}}{1+k\cdot\Delta\text{SSV}}\right)^{\!2}
              - l_P^2\,},
\end{equation}
which reduces to the linear denominator of Eq.~\eqref{eq:PSR} after Planck
normalisation (Version~16, \S A.4).

The step-budget relation~\eqref{eq:budget} recovers time dilation and length
contraction:
\begin{align}
  \Delta\tau &\;=\; t_P\sqrt{1 - v^2/c^2}
  &&\text{(proper-time slowing)},\\
  d_{\rm spatial} &\;=\; l_P\,\frac{v}{c}
  &&\text{(spatial step proportional to velocity)}.
\end{align}
All five predictions of Version~16 (Table~1 of the main paper) follow without
modification.  The Absolute Moment postulate is therefore empirically
consistent with every laboratory test of special relativity, including the
muon storage-ring data already cited in Version~16.

% ══════════════════════════════════════════════════════════════════════════════
\section{Deferred Topics}
\label{sec:deferred}
% ══════════════════════════════════════════════════════════════════════════════

Two topics arise naturally from the present framework but require dedicated
treatment:

\textbf{Chirality.}  The 600-cell lattice admits two chiral realizations
(left- and right-handed H4 Coxeter group).  If the physical universe selected
one realization, this would imprint a systematic handedness on all CP
transits, consistent with the observed left-handed parity violation of the
weak interaction.  Statistical evidence for universal left-handed chirality
across more than 100 empirical phenomena has been analysed using Fisher
combination of $p$-values (Abshier, 2025--2026, GitHub swarm-analysis
repository, $p < 10^{-13}$).  The mechanism by which a chiral nucleation
event could freeze a single realization, and its implications for the
electroweak Lagrangian, are reserved for a companion chirality paper.

\textbf{Quantum tunnelling and entanglement.}  Definition~\ref{def:psr-disp}
identifies soliton SSV superposition as a candidate mechanism for tunnelling
($d > \text{PSR}$).  The address-time vector in the DI-bit string suggests a
mechanism for non-local correlation (entanglement) via shared $t_{\rm abs}$
stamps.  Both topics are reserved for the companion paper on the Born-rule
and quantum-classical bridge.

% ══════════════════════════════════════════════════════════════════════════════
\section{Conclusion}
\label{sec:conclusion}
% ══════════════════════════════════════════════════════════════════════════════

We have established three results for the Absolute Moment postulate of CPP:

\begin{enumerate}
  \item \textbf{Necessity.}  The PCD cycle shows that global DI-bit
    conservation admits no self-consistent locally asynchronous tick
    schedule.  A universal tick at interval $t_P = l_P/c$ is the unique
    compatible schedule (Theorem~\ref{thm:necessity}).

  \item \textbf{Stress-invariance.}  The atemporal Nexus, operating outside
    every Voronoi cell, pins the timelike advance at exactly $l_P$ per tick
    for every CP regardless of local SSV stress, supplying the fixed
    denominator in $\text{PSR}_{\rm eff}$.

  \item \textbf{Causal field propagation and inverse-square falloff.}  Shell
    broadcast at speed $c$ --- one PSR shell per Moment --- distributes the
    GP's fixed SSV quantum over a surface growing as $4\pi r^2$, yielding the
    $1/r^2$ falloff that underpins Coulomb's law and Newtonian gravity,
    while preserving causality and leaving super-PSR channels open for
    tunnelling and entanglement.
\end{enumerate}

The PSR (communication radius) and the displacement step are identified as
two distinct quantities, coinciding only for photons (null geodesic).  The
4D step-budget relation $l_P^2 = (c\,\Delta\tau)^2 + |\mathbf{d}_{\rm
spatial}|^2$ reproduces time dilation and length contraction exactly,
consistent with Version~16 and with all laboratory tests of special
relativity.

This companion paper closes the logical foundation required for the SR
derivation of Version~16 and opens the path to companion papers on stiffness
$C$ from dipole interaction, chirality, and the Born-rule bridge.

% ══════════════════════════════════════════════════════════════════════════════
\section*{References}
% ══════════════════════════════════════════════════════════════════════════════

\begin{enumerate}[label={[\arabic*]}]
  \item Abshier, T.~L. (2026).
    Mechanistic Derivation of Relativistic Effects via Space Stress Vector
    (SSV) in the Dipole Sea.  Version~16 (main paper).

  \item Abshier, T.~L. (2025--2026).
    Conscious Point Physics Series.
    \url{https://hyperphysics.com/papers}

  \item Abshier, T.~L. (2025--2026).
    Swarm analysis of chiral evidence across 100+ empirical phenomena.
    GitHub repository:
    \url{https://github.com/tlabshier/CPP/tree/main/swarm-analysis-chiral_evidence}
\end{enumerate}

\bigskip
\noindent\textbf{GitHub (velocity-projection and geometric-strain routines):}\\
\url{https://github.com/tlabshier/CPP/blob/main/600-cell_special-relativity_emergence/600cell_monte_carlo_voronoi_k_fit.py}

\end{document}
