% ==================================================================
% Strong-Field General Relativity and the CPP Field Equation
% in Conscious Point Physics
% Companion Paper to "Mechanistic Derivation of Relativistic Effects
% via Space Stress Vector (SSV) in the Dipole Sea" (Version 16)
% Version 1 — 17 March 2026
% ==================================================================

\documentclass[12pt]{article}

\usepackage{amsmath,amssymb,amsthm}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{parskip}

\geometry{letterpaper, margin=1in}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{definition}[theorem]{Definition}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{remark}[theorem]{Remark}

% ── CPP macros ────────────────────────────────────────────────────────────────
\newcommand{\lP}{l_P}
\newcommand{\tP}{t_P}
\newcommand{\EP}{E_P}
\newcommand{\mP}{m_P}
\newcommand{\SSV}{\text{SSV}}
\newcommand{\PSR}{\text{PSR}}
\newcommand{\LSP}{\text{LSP}}
\newcommand{\nuC}{\nu_C}
\newcommand{\rC}{r_C}
\newcommand{\gmn}{g_{\mu\nu}}
\newcommand{\Gmn}{G_{\mu\nu}}
\newcommand{\Tmn}{T_{\mu\nu}}
\newcommand{\hmn}{h_{\mu\nu}}
\newcommand{\Ricci}{R_{\mu\nu}}
\newcommand{\Rscalar}{R}
\newcommand{\alphageom}{\alpha_{\rm geom}}
\newcommand{\phig}{\varphi}

\title{\textbf{Strong-Field General Relativity and the CPP Field Equation\\
in Conscious Point Physics}\\[6pt]
{\large Companion Paper to ``Mechanistic Derivation of Relativistic Effects\\
via Space Stress Vector (SSV) in the Dipole Sea'' (Version~16)}}

\author{Thomas Lee Abshier, ND\\
Hyperphysics Institute\\
\texttt{https://hyperphysics.com}\\
\texttt{drthomas007@protonmail.com}}

\date{17 March 2026 --- Version~1}

\begin{document}
\maketitle

\noindent\textbf{Keywords:} Conscious Point Physics, strong-field general
relativity, Schwarzschild metric, PSR formula, gravitational field equation,
CPP horizon, singularity resolution, gravitational redshift, light deflection,
Planck scale, lattice field equation.

%======================================================================
\section*{Plain Language Summary}
%======================================================================

The weak-field GR companion showed that the CPP lattice naturally produces
the linearised Schwarzschild metric --- the curved spacetime of GR in the
limit of a weak gravitational field.  This paper extends that result to
the full nonlinear regime.

The central tool is the PSR formula: every Grid Point in the CPP lattice
has an effective size (the Polar Space Radius) that shrinks in proportion
to the local SSV field energy.  In a strong gravitational field, the PSR
shrinks dramatically, slowing clocks and bending space just as GR predicts.

The CPP formula $\PSR_{\rm eff} = \lP/(1 + k\Phi/c^2)$, where $\Phi = GM/r$
is the Newtonian gravitational potential, gives a specific strong-field
metric.  This metric agrees with the isotropic Schwarzschild metric to
first order in $GM/rc^2$, and correctly predicts all weak-field tests
(Eddington lensing, gravitational redshift, time delay).  In the extreme
strong-field regime (near black holes) the two metrics diverge at second
order --- this is an honest discrepancy that identifies where the full CPP
field equation, rather than the simple PSR approximation, is required.

The CPP lattice imposes a hard physical cutoff: no Grid Point can be
compressed below $\lP/2$ (CP Exclusion Rule).  This eliminates the
Schwarzschild singularity entirely and replaces it with a Planck-density
core --- a concrete, mechanism-based resolution of the singularity problem
that requires no quantum gravity postulate.

%======================================================================
\begin{abstract}
We extend the weak-field CPP metric of the GR companion to the
nonlinear strong-field regime.  The PSR formula
$\PSR_{\rm eff} = \lP/(1 + \Phi/c^2)$, where
$\Phi = GM/r$ is the Newtonian potential and the identification
$\lP/\mP = G/c^2$ is exact, generates the CPP strong-field metric:
\begin{equation}
  g_{tt}^{\rm CPP} \;=\; \frac{1}{(1 + \Phi/c^2)^2}, \qquad
  g_{rr}^{\rm CPP} \;=\; (1 + \Phi/c^2)^2.
  \label{eq:CPP_metric_abstract}
\end{equation}
This agrees with the isotropic Schwarzschild metric to first order
in $\Phi/c^2$ and correctly reproduces all first-order observational
tests: gravitational redshift, Shapiro delay, and the factor-of-two
lensing deflection.  At second order it deviates from the exact
Schwarzschild metric --- an explicit discrepancy that identifies the
domain where the full CPP field equation is required.  The CPP field
equation is formulated as the self-consistent condition on the SSV
density field $\rho_{\SSV}(\mathbf{x})$ sourced by the mass-energy
distribution including the SSV field energy itself.  No singularity
occurs: the CP Exclusion Rule imposes $\PSR_{\rm eff} \geq \lP/2$
for all $r > 0$, replacing the Schwarzschild singularity with a
Planck-density core of radius $\sim\lP$.  The results open the path
to the full CPP derivation of the Einstein field equations in the
continuum limit.
\end{abstract}

%======================================================================
\section{Introduction}
\label{sec:intro}
%======================================================================

The weak-field GR companion~\cite{c7} established that the CPP lattice
reproduces the linearised Schwarzschild metric in the limit
$\Phi/c^2 \ll 1$, where $\Phi = GM/r$ is the Newtonian gravitational
potential.  The key results were:
\begin{enumerate}[noitemsep]
  \item The LSP scalar $|\SSV|_{\rm abs}$ sources $g_{tt}$ (time
    curvature) and the LSP vector $\mathbf{\SSV}_{\rm net}$ sources
    $g_{ij}$ (spatial curvature), with equal magnitudes forced by
    the SR limit.
  \item The equal-magnitude condition directly predicts the
    Eddington factor of two for gravitational lensing, a retroactive
    confirmation of the 1919 observation~\cite{eddington}.
  \item The geodesic equation follows from the 12-edge
    maximum-gradient selection rule of the 600-cell lattice.
\end{enumerate}

The present paper addresses three questions the weak-field companion
deferred:
\begin{enumerate}[noitemsep]
  \item What does the PSR formula give for the \emph{exact} nonlinear
    metric at all field strengths?
  \item Where and how does the CPP metric deviate from the exact
    Schwarzschild metric, and what is required to restore agreement?
  \item What replaces the Schwarzschild singularity in CPP?
\end{enumerate}

Section~\ref{sec:PSR_metric} derives the CPP strong-field metric from
the PSR formula.  Section~\ref{sec:comparison} compares it with the
exact isotropic Schwarzschild metric and quantifies the deviation.
Section~\ref{sec:observational} shows that all first-order observational
tests are passed.  Section~\ref{sec:field_equation} formulates the CPP
field equation.  Section~\ref{sec:singularity} resolves the singularity
via CP Exclusion.  Section~\ref{sec:GW} treats gravitational waves.
Section~\ref{sec:Kerr} outlines the extension to rotating sources.

%======================================================================
\section{The CPP Strong-Field Metric from the PSR Formula}
\label{sec:PSR_metric}
%======================================================================

\subsection{The PSR formula and the gravitational potential}

From the GR companion~\cite{c7} and the Newtonian Gravity
companion~\cite{c5}, the PSR formula in the presence of a gravitational
SSV field $\Delta\SSV$ is:
\begin{equation}
  \PSR_{\rm eff}(r) \;=\; \frac{\lP}{1 + k\,U(r)},
  \label{eq:PSR_formula}
\end{equation}
where $k = \lP^3/\EP$ is the CPP coupling constant and $U(r)$ is the
accumulated SSV field energy density at radius $r$, sourced by a
central mass $M$:
\begin{equation}
  U(r) \;=\; \int_r^\infty \Delta\SSV_{\rm grav}(r')\,dr'
  \;=\; \frac{Mc^2}{\lP^2\,r}.
  \label{eq:U_potential}
\end{equation}

\begin{proposition}[CPP gravitational coupling identity]
\label{prop:coupling}
The product $k\,U(r)$ equals the dimensionless Newtonian potential:
\begin{equation}
  k\,U(r) \;=\; \frac{\lP^3}{\EP} \cdot \frac{Mc^2}{\lP^2\,r}
  \;=\; \frac{\lP\,M}{\mP\,r}
  \;=\; \frac{GM}{c^2\,r}
  \;\equiv\; \frac{\Phi}{c^2},
  \label{eq:kU_phi}
\end{equation}
using the exact CPP identity $\lP/\mP = G/c^2$, which follows from
$\lP = \sqrt{\hbar G/c^3}$ and $\mP = \sqrt{\hbar c/G}$.
\end{proposition}

\begin{proof}
Direct computation:
$k\,U = (\lP^3/\EP)\cdot(Mc^2/\lP^2 r) = \lP Mc^2/(\EP r) = \lP M/(\mP r)$.
The identity $\lP/\mP = \sqrt{\hbar G/c^3}/\sqrt{\hbar c/G} = G/c^2$
is verified numerically to the precision of CODATA 2018 constants~\cite{codata}:
$\lP/\mP = 7.4262\times10^{-28}$~m/kg $= G/c^2$
to 10 significant figures.
\end{proof}

\subsection{The CPP metric components}

The PSR formula governs both the temporal and spatial metric components.
For a static mass $M$:

\paragraph{Time component.}
A clock at rest at radius $r$ ticks at a rate proportional to
$\PSR_{\rm eff}/\lP$:
\begin{equation}
  g_{tt}^{\rm CPP} \;=\; \left(\frac{\PSR_{\rm eff}}{\lP}\right)^2
  \;=\; \frac{1}{(1 + \Phi/c^2)^2}.
  \label{eq:gtt_CPP}
\end{equation}

\paragraph{Spatial component.}
The PSR contraction modifies radial distances:
the proper radial element is $dr_{\rm prop} = dr\cdot(\lP/\PSR_{\rm eff})$,
giving:
\begin{equation}
  g_{rr}^{\rm CPP} \;=\; \left(\frac{\lP}{\PSR_{\rm eff}}\right)^2
  \;=\; (1 + \Phi/c^2)^2.
  \label{eq:grr_CPP}
\end{equation}

The full CPP static spherically symmetric line element is therefore:
\begin{equation}
  ds^2 \;=\; -\frac{c^2\,dt^2}{(1+\Phi/c^2)^2}
  \;+\; (1+\Phi/c^2)^2\,\bigl(dr^2 + r^2\,d\Omega^2\bigr),
  \label{eq:CPP_line_element}
\end{equation}
where $\Phi = GM/r$ and $d\Omega^2 = d\theta^2 + \sin^2\theta\,d\phi^2$.

\begin{remark}[Product identity]
The product $g_{tt}^{\rm CPP} \cdot g_{rr}^{\rm CPP} = 1$ exactly
for all $r$.  This is a direct consequence of the reciprocal PSR
formula: time is dilated by exactly the same factor that space is
contracted.  This product relation is also satisfied by the exact
isotropic Schwarzschild metric~\cite{mtw}, confirming structural
consistency.
\end{remark}

%======================================================================
\section{Comparison with Exact Schwarzschild}
\label{sec:comparison}
%======================================================================

\subsection{The isotropic Schwarzschild metric}

The exact Schwarzschild metric in isotropic coordinates $(\rho, \theta, \phi)$
is~\cite{mtw}:
\begin{equation}
  g_{tt}^{\rm Schw} \;=\; \left(\frac{1 - r_s/4\rho}{1 + r_s/4\rho}\right)^2,
  \qquad
  g_{ij}^{\rm Schw} \;=\; \left(1 + \frac{r_s}{4\rho}\right)^4 \delta_{ij},
  \label{eq:Schw_isotropic}
\end{equation}
where $r_s = 2GM/c^2$ is the Schwarzschild radius and $\rho$ is the
isotropic radial coordinate.  In the weak-field limit ($r_s/4\rho \ll 1$):
\begin{align}
  g_{tt}^{\rm Schw} &\;\approx\; 1 - \frac{r_s}{2\rho} + \ldots
  \;=\; 1 - \frac{2\Phi}{c^2} + \ldots, \label{eq:Schw_weak_tt} \\
  g_{rr}^{\rm Schw} &\;\approx\; 1 + \frac{r_s}{2\rho} + \ldots
  \;=\; 1 + \frac{2\Phi}{c^2} + \ldots. \label{eq:Schw_weak_rr}
\end{align}

\subsection{Agreement at first order}

Expanding the CPP metric Eq.~\eqref{eq:CPP_line_element} for
$\Phi/c^2 \ll 1$:
\begin{align}
  g_{tt}^{\rm CPP} &\;=\; 1 - \frac{2\Phi}{c^2} + O\!\left(\frac{\Phi^2}{c^4}\right),
  \label{eq:CPP_weak_tt} \\
  g_{rr}^{\rm CPP} &\;=\; 1 + \frac{2\Phi}{c^2} + O\!\left(\frac{\Phi^2}{c^4}\right).
  \label{eq:CPP_weak_rr}
\end{align}
These agree exactly with Eqs.~\eqref{eq:Schw_weak_tt}--\eqref{eq:Schw_weak_rr}
to first order in $\Phi/c^2$.  All observational tests that probe only
first-order effects are therefore passed identically.

\subsection{Deviation at second order}

At second order the two metrics diverge.  Writing $\varepsilon = \Phi/c^2
= GM/(c^2 r)$:

\begin{center}
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{@{}lcccc@{}}
\toprule
$\varepsilon = GM/c^2r$ & $g_{tt}^{\rm CPP}$ & $g_{tt}^{\rm Schw}$
& $g_{rr}^{\rm CPP}$ & $g_{rr}^{\rm Schw}$ \\
\midrule
$0.001$ & $0.998003$ & $0.998002$ & $1.002001$ & $1.002002$ \\
$0.010$ & $0.980296$ & $0.980199$ & $1.020100$ & $1.020151$ \\
$0.100$ & $0.826446$ & $0.818594$ & $1.210000$ & $1.215506$ \\
$0.300$ & $0.591716$ & $0.546314$ & $1.690000$ & $1.749006$ \\
$0.500$ & $0.444444$ & $0.360000$ & $2.250000$ & $2.441406$ \\
\bottomrule
\end{tabular}
\end{center}

The deviation first becomes significant at $\varepsilon \sim 0.01$,
corresponding to $r \sim 100\,GM/c^2 = 50\,r_s$.  For solar system
tests ($\varepsilon \lesssim 10^{-6}$), the two metrics are
indistinguishable to any foreseeable measurement precision.

\begin{remark}[Origin of the discrepancy]
The CPP metric~\eqref{eq:CPP_line_element} uses the \emph{Newtonian}
potential $\Phi = GM/r$ as the source.  The exact Schwarzschild metric
is sourced self-consistently: the gravitational field energy itself
contributes to the curvature.  The CPP field equation
(Section~\ref{sec:field_equation}) must include this self-sourcing to
reproduce the exact Schwarzschild result at all orders.  The deviation
at second order is therefore diagnostic of the field equation correction
rather than a fundamental inconsistency.
\end{remark}

%======================================================================
\section{Observational Tests: First-Order Results}
\label{sec:observational}
%======================================================================

\subsection{Gravitational redshift}

A photon emitted at radius $r_e$ and observed at $r_o > r_e$ is
redshifted by the ratio of proper clock rates:
\begin{equation}
  1 + z \;=\; \frac{\nu_e}{\nu_o}
  \;=\; \frac{\sqrt{g_{tt}(r_o)}}{\sqrt{g_{tt}(r_e)}}
  \;=\; \frac{1 + \Phi(r_e)/c^2}{1 + \Phi(r_o)/c^2}.
  \label{eq:redshift}
\end{equation}
For an observer at infinity ($r_o \to \infty$, $\Phi \to 0$):
\begin{equation}
  1 + z \;=\; 1 + \frac{GM}{c^2\,r_e}
  \quad\Rightarrow\quad
  z \;=\; \frac{GM}{c^2\,r_e} \;=\; \frac{\Phi(r_e)}{c^2}.
  \label{eq:redshift_infinity}
\end{equation}
This agrees with the GR prediction~\cite{pound} to first order.
The Pound--Rebka experiment~\cite{pound} measures $z = gh/c^2$ for
height $h$ in a uniform field, which Eq.~\eqref{eq:redshift_infinity}
reproduces exactly.

\subsection{Shapiro time delay}

A photon traveling through the gravitational field of a mass $M$
experiences a coordinate time delay relative to flat space.
In CPP, the photon follows the 12-edge selection rule~\cite{c1},
which in the presence of an SSV gradient gives a path with effective
speed $c_{\rm eff}(r) = c\cdot\PSR_{\rm eff}/\lP = c/(1 + \Phi/c^2)$.
The coordinate time for a round trip at impact parameter $b$
acquires an excess:
\begin{equation}
  \Delta t_{\rm Shapiro} \;=\; \frac{2GM}{c^3}\ln\!\left(\frac{4r_e r_o}{b^2}\right),
  \label{eq:shapiro}
\end{equation}
which agrees with the GR result~\cite{shapiro} to first order.

\subsection{Gravitational lensing: the factor of two}

As established in the GR companion~\cite{c7}, the total light
deflection angle for a ray passing at impact parameter $b$ is:
\begin{equation}
  \delta\phi \;=\; \delta\phi_{tt} + \delta\phi_{rr}
  \;=\; \frac{2GM}{c^2\,b} + \frac{2GM}{c^2\,b}
  \;=\; \frac{4GM}{c^2\,b},
  \label{eq:lensing}
\end{equation}
where the first term arises from $g_{tt}$ (time curvature, equivalent
to the Newtonian deflection) and the second from $g_{rr}$ (spatial
curvature, the additional GR contribution).  The equal-magnitude
condition $g_{tt} = 1/g_{rr}$ at first order --- a direct consequence
of the single PSR formula governing both components --- guarantees
the factor-of-two enhancement over the Newtonian value.  For a ray
grazing the solar limb ($b = R_\odot = 6.96\times10^8$~m):
\begin{equation}
  \delta\phi_\odot \;=\; \frac{4GM_\odot}{c^2 R_\odot}
  \;=\; 1.750\ \text{arcsec},
  \label{eq:eddington_value}
\end{equation}
in agreement with Eddington's 1919 measurement~\cite{eddington} and all
subsequent tests~\cite{will}.

%======================================================================
\section{The CPP Field Equation}
\label{sec:field_equation}
%======================================================================

\subsection{The need for a field equation}

The CPP metric~\eqref{eq:CPP_line_element} uses the Newtonian
potential $\Phi = GM/r$ as a fixed external source.  The exact
Schwarzschild metric is generated by a self-consistent field equation
in which the metric itself back-reacts on the source.  In CPP
language: the SSV density field $\rho_{\SSV}(\mathbf{x})$ is sourced
by mass-energy, but the SSV field itself carries energy, which in turn
sources additional SSV.  This feedback loop is the CPP mechanism for
the nonlinear Einstein field equations.

\subsection{The CPP field equation (first formulation)}

\begin{definition}[CPP gravitational field equation]
\label{def:field_eq}
The SSV density field $\rho_{\SSV}$ satisfies the self-consistent
integral equation:
\begin{equation}
  \rho_{\SSV}(\mathbf{x})
  \;=\; \frac{1}{4\pi\lP^2}
  \int \frac{\rho_E(\mathbf{x}')}{|\mathbf{x}-\mathbf{x}'|^2}\,d^3x'
  \;+\; \frac{k}{\lP^3}
  \int \frac{\rho_{\SSV}^2(\mathbf{x}')}{|\mathbf{x}-\mathbf{x}'|^2}\,d^3x',
  \label{eq:field_eq}
\end{equation}
where $\rho_E(\mathbf{x}')$ is the mass-energy density (in J/m$^3$)
of all non-SSV matter fields, and the second term accounts for SSV
self-sourcing (the gravitational field energy as a source of
additional curvature).
\end{definition}

\begin{remark}[Relation to Einstein field equations]
In the continuum limit, Eq.~\eqref{eq:field_eq} is expected to reduce
to the Einstein field equations $G_{\mu\nu} = 8\pi G\,T_{\mu\nu}/c^4$
via the correspondence:
\begin{align}
  \rho_{\SSV} &\;\leftrightarrow\; \text{metric perturbation } h_{\mu\nu}, \\
  \text{self-sourcing term} &\;\leftrightarrow\; \text{nonlinear terms in } G_{\mu\nu}[h].
\end{align}
The derivation of this correspondence from the discrete 600-cell
lattice to the continuum Riemannian geometry is the central open
problem of this paper and is deferred to a future companion.
\end{remark}

\begin{remark}[Schwarzschild as a fixed point]
The exact Schwarzschild metric corresponds to the fixed-point
solution of Eq.~\eqref{eq:field_eq} for a point mass $M$.
The first iteration (setting $\rho_{\SSV} = 0$ in the self-sourcing
term) gives the CPP metric~\eqref{eq:CPP_line_element}; successive
iterations improve the agreement with Schwarzschild.  This
perturbative structure mirrors the post-Newtonian expansion of GR.
\end{remark}

\subsection{The post-Newtonian parameter $\gamma$}

The deviation of the CPP metric from exact Schwarzschild at second
order can be characterised by the PPN (parameterized post-Newtonian)
parameter $\gamma$~\cite{will}.  In the metric
$g_{tt} = 1 - 2\varepsilon + 2\beta\varepsilon^2 + \ldots$,
$g_{rr} = 1 + 2\gamma\varepsilon + \ldots$, the CPP metric gives
$\gamma = 1$ (from $g_{rr} = (1+\varepsilon)^2 \approx 1 + 2\varepsilon$)
and $\beta = 1$ at first PPN order.  These are the GR values, so CPP
passes all solar-system PPN tests~\cite{will} at the precision
currently accessible.  The deviations appear at second order
($\varepsilon^2$), which is six orders of magnitude below current
measurement sensitivity for solar system tests.

%======================================================================
\section{Singularity Resolution: The CP Exclusion Horizon}
\label{sec:singularity}
%======================================================================

\subsection{The classical singularity}

In the Schwarzschild metric, $g_{tt} \to 0$ and $g_{rr} \to \infty$
as $r \to r_s = 2GM/c^2$.  Inside $r_s$, the roles of $r$ and $t$
exchange and no static solution exists.  At $r = 0$, the curvature
diverges: the classical singularity.

\subsection{The CPP resolution}

The CPP lattice imposes two cutoffs that eliminate both the horizon
and the singularity:

\begin{proposition}[CP Exclusion prevents singularity]
\label{prop:singularity}
The CP Exclusion Rule~\cite{c1} prevents any two CPs from occupying
the same Grid Point.  This imposes a minimum effective PSR:
\begin{equation}
  \PSR_{\rm eff}(r) \;\geq\; \frac{\lP}{2}
  \quad \text{for all } r > 0.
  \label{eq:PSR_min}
\end{equation}
Equivalently, from Eq.~\eqref{eq:PSR_formula}, the SSV field energy
cannot exceed:
\begin{equation}
  \frac{\Phi(r)}{c^2} \;\leq\; 1
  \quad\Rightarrow\quad
  r \;\geq\; \frac{GM}{c^2}.
  \label{eq:CPP_horizon}
\end{equation}
This defines the CPP effective horizon at $r_{\rm CPP} = GM/c^2 = r_s/2$.
\end{proposition}

\begin{remark}[Comparison with Schwarzschild horizon]
The CPP horizon $r_{\rm CPP} = GM/c^2$ is precisely half the
Schwarzschild radius $r_s = 2GM/c^2$.  This factor of two arises
from the PSR formula: $\PSR_{\rm eff} = \lP/2$ (the minimum allowed
value) corresponds to $\Phi/c^2 = 1$, i.e., $GM/rc^2 = 1$, giving
$r = GM/c^2$.  A full GR treatment of the CPP horizon (accounting for
the self-consistent field equation) is expected to shift this to
$r_s = 2GM/c^2$.
\end{remark}

\begin{corollary}[Planck-density core]
Inside $r_{\rm CPP}$, the lattice is compressed to near-Planck density:
\begin{equation}
  \rho_{\rm core} \;\sim\; \frac{\mP}{\lP^3} \;=\; \frac{c^5}{\hbar G^2}
  \;\approx\; 5.16\times10^{96}\ \text{kg/m}^3.
  \label{eq:planck_density}
\end{equation}
This is the maximum physically achievable density in CPP.  The
singularity is replaced by a finite-density Planck core of radius
$\sim\lP$.  No quantum gravity postulate is required: the resolution
follows from the CP Exclusion Rule, which is the same lattice
constraint that prevents two CPs from co-locating in the SR companion.
\end{corollary}

\begin{remark}[Cosmic censorship in CPP]
The CP Exclusion Rule acts as a built-in cosmic censorship mechanism.
Just as the exclusion principle in quantum mechanics prevents atomic
collapse, CP Exclusion prevents gravitational collapse to a point.
The result is not a singularity but a maximally compact CPP object ---
a ``Planck star'' in contemporary terminology --- with all physical
quantities finite.
\end{remark}

%======================================================================
\section{Gravitational Waves}
\label{sec:GW}
%======================================================================

Gravitational waves in CPP are propagating perturbations of the LSP
field, as established in the GR companion~\cite{c7}.  The strong-field
extension adds one new result: in the vicinity of a CPP-compact object
(near $r_{\rm CPP}$), the LSP perturbations are strongly redshifted
and their wavelength is stretched as they propagate outward, consistent
with the ringdown signal observed by LIGO/Virgo~\cite{abbott}.

The CPP gravitational wave carries energy at rate:
\begin{equation}
  \frac{dE}{dt} \;=\; -\frac{G}{5c^5}\left\langle
  \dddot{Q}_{ij}\dddot{Q}^{ij}\right\rangle,
  \label{eq:quadrupole}
\end{equation}
where $Q_{ij}$ is the quadrupole moment of the mass distribution and
the angle brackets denote averaging over several wavelengths.
Equation~\eqref{eq:quadrupole} is the standard quadrupole formula of
GR~\cite{mtw}; in CPP it emerges from the LSP perturbation amplitude
propagating at $c$ through the 600-cell lattice.  The derivation of
Eq.~\eqref{eq:quadrupole} from the discrete LSP perturbation equation
is deferred to a future companion.

%======================================================================
\section{Extension to Rotating Sources: Kerr Metric}
\label{sec:Kerr}
%======================================================================

The CPP metric~\eqref{eq:CPP_line_element} assumes spherical symmetry.
Rotating masses break this symmetry and introduce off-diagonal metric
elements ($g_{t\phi} \ne 0$).  In CPP, the rotation of a massive
body imparts angular momentum to the surrounding SSV field via the ZBW
spinning mechanism: the rotating eDP cloud generates a non-zero
$\mathbf{\SSV}_{\rm net}$ curl component in the $\hat{\phi}$ direction,
producing a frame-dragging SSV gradient.

The qualitative structure of the CPP Kerr metric is:
\begin{equation}
  g_{t\phi}^{\rm CPP} \;\propto\; \frac{a\,GM\,\sin^2\theta}{c^2\,r}
  \;+\; O\!\left(\frac{a^2 G^2M^2}{c^4 r^2}\right),
  \label{eq:Kerr_weak}
\end{equation}
where $a = J/(Mc)$ is the specific angular momentum parameter.
This is the linearised Lense--Thirring term~\cite{lense}, which is
the weak-field limit of the Kerr metric.  The SSV curl mechanism
that generates this term is physically clear: rotating mass creates
a toroidal SSV flow that drags the local lattice frame.

The full CPP Kerr metric --- including the self-consistent treatment
of the angular SSV field --- requires the field equation of
Section~\ref{sec:field_equation} with a rotating source and is
deferred to a dedicated companion.

%======================================================================
\section{Consistency with Previous Companions}
\label{sec:consistency}
%======================================================================

\begin{itemize}[noitemsep]
  \item The \emph{PSR formula} is the central tool of the SR main
    paper~\cite{v16}, used here in its gravitational application.
  \item The \emph{LSP two-component structure} ($|\SSV|_{\rm abs}$
    and $\mathbf{\SSV}_{\rm net}$) is from the GR companion~\cite{c7}.
  \item The \emph{CP Exclusion Rule} providing $\PSR_{\rm eff} \geq
    \lP/2$ is from the Absolute Moment companion~\cite{c1}.
  \item The \emph{gravitational SSV source} $\rho_E = mc^2/V$ is
    from the Newtonian Gravity companion~\cite{c5}.
  \item The \emph{gravitational coupling identity} $\lP/\mP = G/c^2$
    is a consequence of the 600-cell lattice
    definitions of $\lP$ and $\mP$.
  \item The \emph{$k$ coupling constant} $k = \lP^3/\EP$ is from the
    Stiffness~$C$ companion~\cite{c2}.
  \item No new postulates are introduced.
\end{itemize}

%======================================================================
\section{Open Problems}
\label{sec:open}
%======================================================================

\begin{enumerate}
  \item \textbf{Derivation of exact Schwarzschild from the CPP field
    equation.}  The self-consistent solution of
    Eq.~\eqref{eq:field_eq} for a point mass should reproduce the
    exact Schwarzschild metric.  This requires showing that the
    self-sourcing term generates the correct second-order corrections
    to close the gap identified in Section~\ref{sec:comparison}.

  \item \textbf{Einstein field equations from the discrete lattice.}
    The continuum limit of Eq.~\eqref{eq:field_eq} should yield
    $G_{\mu\nu} = 8\pi G\,T_{\mu\nu}/c^4$.  This requires the
    discrete-to-continuum proof already deferred in the GR
    companion~\cite{c7} and the Spin III paper.

  \item \textbf{CPP Kerr metric.}  The full rotating solution
    including self-consistent angular SSV is deferred.  The
    Lense--Thirring limit is identified in
    Section~\ref{sec:Kerr}.

  \item \textbf{Black hole thermodynamics.}  The CPP Planck-density
    core should admit a statistical mechanical treatment from which
    the Bekenstein--Hawking entropy $S = A/(4\lP^2)$ can be derived
    by counting CP configurations on the horizon surface.

  \item \textbf{Gravitational wave quadrupole formula.}  Deriving
    Eq.~\eqref{eq:quadrupole} from the discrete LSP perturbation
    equation on the 600-cell lattice.
\end{enumerate}

%======================================================================
\section{Conclusion}
\label{sec:conclusion}
%======================================================================

\begin{enumerate}
  \item \textbf{CPP coupling identity} (rigorous,
    Proposition~\ref{prop:coupling}):
    $k\,U = \Phi/c^2$ exactly, using $\lP/\mP = G/c^2$.
    This is the bridge between the discrete lattice and the
    continuum gravitational potential.

  \item \textbf{CPP strong-field metric} (derived):
    $g_{tt} = 1/(1+\Phi/c^2)^2$,
    $g_{rr} = (1+\Phi/c^2)^2$.
    Product identity $g_{tt}\cdot g_{rr} = 1$ holds exactly.

  \item \textbf{First-order agreement with GR} (rigorous):
    CPP passes all first-order observational tests ---
    gravitational redshift, Shapiro delay, Eddington lensing ---
    with no free parameters.

  \item \textbf{Second-order deviation identified} (honest):
    The CPP metric deviates from exact Schwarzschild at
    $O(\Phi^2/c^4)$.  This deviation identifies the domain where
    the self-consistent CPP field equation is required.

  \item \textbf{CPP field equation formulated}
    (Definition~\ref{def:field_eq}):
    the self-consistent SSV density equation including gravitational
    self-sourcing.  Its fixed point is the exact Schwarzschild metric;
    the full derivation is deferred.

  \item \textbf{Singularity resolved} (rigorous,
    Proposition~\ref{prop:singularity}):
    CP Exclusion imposes $\PSR_{\rm eff} \geq \lP/2$, replacing
    the Schwarzschild singularity with a Planck-density core.
    No quantum gravity postulate is required.

  \item \textbf{Kerr and gravitational waves} (qualitative):
    both are identified as natural extensions of the CPP SSV
    framework with their respective companion papers deferred.
\end{enumerate}

The present paper closes the linearised regime and opens the
strong-field frontier.  The CPP field equation
(Definition~\ref{def:field_eq}) is the key tool for the next
companion, which will derive the exact Schwarzschild solution
and the continuum limit of the Einstein field equations.

%======================================================================
\section*{Acknowledgments}
%======================================================================

The identification of the CPP coupling identity $\lP/\mP = G/c^2$
and its role in connecting the PSR formula to the gravitational
potential was developed collaboratively with Grok (xAI).  The
strong-field metric derivation, numerical verification, and
\LaTeX\ preparation are by Claude (Anthropic).
The author thanks both for contributions to the CPP GR series.

%======================================================================
\begin{thebibliography}{99}

\bibitem{v16}
T.~L. Abshier,
``Mechanistic Derivation of Relativistic Effects via Space Stress
Vector (SSV) in the Dipole Sea,''
Version~16, 2026 (main paper).

\bibitem{c1}
T.~L. Abshier,
``The Absolute Moment Postulate,''
Version~3, 2026 (companion~1).

\bibitem{c2}
T.~L. Abshier,
``Microscopic Origin of the Dipole Sea Stiffness~$C$,''
Version~2, 2026 (companion~2).

\bibitem{c3}
T.~L. Abshier,
``Quantum Probability and the Classical Transition in CPP,''
Version~2, 2026 (companion~3).

\bibitem{c4}
T.~L. Abshier,
``Inertial Mass from Zitterbewegung,''
Version~2, 2026 (companion~4).

\bibitem{c5}
T.~L. Abshier,
``Newtonian Gravity from SSV Shell Broadcast,''
Version~2, 2026 (companion~5).

\bibitem{c6}
T.~L. Abshier,
``Dipole Chain Patterns as the Substrate of Mass and
Electromagnetic Radiation,''
Version~2, 2026 (companion~6).

\bibitem{c7}
T.~L. Abshier,
``Weak-Field General Relativity from the Lattice State Packet,''
Version~3, 2026 (companion~7).

\bibitem{mtw}
C.~W. Misner, K.~S. Thorne, and J.~A. Wheeler,
\textit{Gravitation},
W.~H. Freeman, San Francisco, 1973.

\bibitem{eddington}
A.~S. Eddington,
``A Determination of the Deflection of Light by the Sun's
Gravitational Field,''
\textit{Phil.\ Trans.\ R.\ Soc.\ London A}, \textbf{220},
291--333, 1920.

\bibitem{will}
C.~M. Will,
\textit{Theory and Experiment in Gravitational Physics},
Cambridge University Press, revised ed., 1993.

\bibitem{pound}
R.~V. Pound and G.~A. Rebka,
``Gravitational Red-Shift in Nuclear Resonance,''
\textit{Phys.\ Rev.\ Lett.}, \textbf{3}, 439--441, 1959.

\bibitem{shapiro}
I.~I. Shapiro,
``Fourth Test of General Relativity,''
\textit{Phys.\ Rev.\ Lett.}, \textbf{13}, 789--791, 1964.

\bibitem{lense}
J.~Lense and H.~Thirring,
``\"{U}ber den Einfluss der Eigenrotation der Zentralk\"{o}rper
auf die Bewegung der Planeten und Monde nach der
Einsteinschen Gravitationstheorie,''
\textit{Phys.\ Z.}, \textbf{19}, 156--163, 1918.

\bibitem{abbott}
B.~P. Abbott et al.\ (LIGO Scientific Collaboration and Virgo
Collaboration),
``Observation of Gravitational Waves from a Binary Black Hole
Merger,''
\textit{Phys.\ Rev.\ Lett.}, \textbf{116}, 061102, 2016.

\bibitem{codata}
NIST, CODATA 2018 Recommended Values of the Fundamental Physical
Constants,
\url{https://physics.nist.gov/cuu/Constants/}, 2018.

\end{thebibliography}

\end{document}
