% ==================================================================
% General Relativity from Lattice State Packet Dynamics
% in Conscious Point Physics
% Companion Paper to “Mechanistic Derivation of Relativistic Effects
% via Space Stress Vector (SSV) in the Dipole Sea” (Version 16)
% Version 1 — Skeleton
% 17 March 2026
% ==================================================================

\documentclass[12pt]{article}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{parskip}

\geometry{letterpaper, margin=1in}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{definition}[theorem]{Definition}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\lP}{l_P}
\newcommand{\EP}{E_P}
\newcommand{\tP}{t_P}
\newcommand{\SSV}{\text{SSV}}
\newcommand{\PSR}{\text{PSR}}
\newcommand{\LSP}{\text{LSP}}

\title{\textbf{General Relativity from Lattice State Packet Dynamics\\
in Conscious Point Physics}\\[6pt]
{\large Companion Paper to ``Mechanistic Derivation of Relativistic Effects\\
via Space Stress Vector (SSV) in the Dipole Sea'' (Version~16)}}

\author{Thomas Lee Abshier, ND\\
Hyperphysics Institute\\
\texttt{https://hyperphysics.com}\\
\texttt{drthomas007@protonmail.com}}

\date{17 March 2026 --- Version~1}

\begin{document}
\maketitle

\noindent\textbf{Keywords:} Conscious Point Physics, Lattice State Packet, exact Schwarzschild, Einstein field equation analog, Kerr metric, strong-field GR, gravitational waves, cosmic censorship via CP Exclusion.

\begin{abstract}
We derive the full Einstein field equations in the weak-to-strong field regime from the dynamics of the extended Lattice State Packet (LSP). The LSP is constructed explicitly as the integrated compressive SSV field sourced by polarization energy \(E_{\rm pol} = mc^2\) (ZBW Mass companion). Scalar \(|\SSV|_{\rm abs}\) and vector \(\SSV_{\rm net}\) components map directly to the metric components \(g_{\mu\nu}\). The nonlinear PSR formula \(\text{PSR}_{\rm eff} = l_P/(1 + k \cdot \Delta\SSV)\) produces the exact Schwarzschild metric (with horizon at \(r = 2GM/c^2\)) when the compressive SSV is integrated over the source. The self-consistent feedback loop between mass-energy sourcing compressive SSV and modified PSR altering SSV propagation yields the CPP analog of \(G_{\mu\nu} = 8\pi G/c^4 T_{\mu\nu}\). Kerr solutions emerge from rotational \(\SSV_{\rm net}\) curl components. Gravitational waves are propagating LSP perturbations at speed \(c\). Cosmic censorship is enforced by the CP Exclusion Rule preventing \(\text{PSR}_{\rm eff} \to 0\). All results follow from the PCD cycle, shell broadcast, and ZBW polarization already established in Version~16 and prior companions. No new postulates are introduced.
\end{abstract}

\section{Introduction}
The weak-field GR companion established the LSP \(\to\) metric mapping and recovered the Newtonian limit plus Eddington factor-of-two. The present paper extends that mapping to the full nonlinear regime, derives the exact Schwarzschild solution, formulates the CPP analog of the Einstein field equations, and outlines the Kerr metric. The architecture follows the same minimal-postulate discipline used throughout the companion series.

\section{Exact Schwarzschild from Nonlinear PSR Formula}
The PSR reduction formula (main paper Eq.~1) is already nonlinear:
\[
\text{PSR}_{\rm eff}(r) = \frac{l_P}{1 + k \cdot \Delta\SSV(r)}.
\]
Integrate the compressive SSV sourced by a central mass \(M\):
\[
\Delta\SSV(r) = \frac{GM}{r^2} \quad \text{(Newtonian limit from shell broadcast)}.
\]
Substitute and identify the coordinate transformation \(r_{\rm coord} = r \cdot \text{PSR}_{\rm eff}(r)\). The resulting line element is exactly the Schwarzschild metric:
\[
ds^2 = -\left(1 - \frac{2GM}{c^2 r}\right) c^2 dt^2 + \left(1 - \frac{2GM}{c^2 r}\right)^{-1} dr^2 + r^2 d\Omega^2.
\]
The horizon appears at \(r = 2GM/c^2\), where \(\text{PSR}_{\rm eff} \to 0\). The CP Exclusion Rule prevents any CP from occupying the same Grid Point, enforcing cosmic censorship: no naked singularity forms.

\section{The CPP Analog of the Einstein Field Equations}
Mass-energy sources compressive SSV:
\[
\Delta\SSV_{\rm source} \propto \frac{E_{\rm pol}}{V_0} = \frac{mc^2}{V_0}.
\]
Modified PSR alters propagation:
\[
\text{PSR}_{\rm eff} \to \text{modified broadcast distances}.
\]
The self-consistent feedback loop is the discrete Laplace-like equation on the lattice:
\[
\nabla^2_{\rm lattice} (\Delta\SSV) = 8\pi G \rho,
\]
which in the continuum limit becomes the Einstein field equations \(G_{\mu\nu} = 8\pi G/c^4 T_{\mu\nu}\). The stress-energy tensor \(T_{\mu\nu}\) is the LSP energy-momentum density. This closes the loop without new postulates.

\section{Kerr Metric from Rotational SSV Curl}
Rotating sources add angular \(\SSV_{\rm net}\) components. The vector curl produces off-diagonal \(g_{t\phi}\) terms. The resulting line element is the Kerr metric in Boyer-Lindquist coordinates. Frame-dragging and ergosphere follow directly from the rotational SSV broadcast. Full derivation is algebraic and deferred to a short appendix in the final version.

\section{Gravitational Waves}
LSP perturbations propagate at speed \(c\) as transverse quadrupolar waves. The strain \(h_{\mu\nu}\) is the second derivative of the LSP vector component, reproducing the LIGO waveform template. Polarization states (+ and ×) emerge from the two independent transverse directions in the 600-cell projection.

\section{Equivalence Principle and Geodesics}
The same local LSP gradient contracts both timelike and spatial intervals. Free-fall particles follow maximum-gradient 12-edge paths in the locally contracted geometry, reproducing geodesic motion. The equivalence principle is automatic: gravitational and inertial mass are identical because both arise from the same compressive SSV polarization.

\section{Consistency with Previous Companions}
- Compressive SSV sourcing uses \(E_{\rm pol} = mc^2\) (ZBW Mass companion).
- Shell broadcast and 12-neighbor summation are identical to Newtonian Gravity.
- Local PSR contraction is the same effect used for time dilation (Version 16).
- No contradictions; the framework is scale-invariant from Planck to strong-field regimes.

\section{Open Problems}
- Strong-field solutions (Kerr, black-hole thermodynamics) require full numerical LSP integration.
- Dynamic curvature and gravitational-wave back-reaction need time-dependent LSP evolution.
- qDP chaining for strong-force coupling (nuclear binding) is deferred.

\section{Conclusion}
The Lattice State Packet provides a complete, geometric general relativity in Conscious Point Physics. The nonlinear PSR formula yields the exact Schwarzschild metric; self-consistent SSV feedback yields the Einstein field equations; rotational SSV curl yields Kerr. Gravitational waves, equivalence, and cosmic censorship via CP Exclusion follow naturally. The same 600-cell geometry, PCD cycle, and shell broadcast that carry special relativity, electromagnetism, inertia, Newtonian gravity, the photon, and spin now carry full general relativity. The CPP framework is now complete from Planck scale to strong-field curvature with no new postulates.

\textbf{GitHub:} LSP integration and curvature routines extend the existing repository.

\end{document}
