% ==================================================================
% Newtonian Gravity from SSV Shell Broadcast
% A Mechanistic Derivation in Conscious Point Physics
% Companion Paper to “Mechanistic Derivation of Relativistic Effects
% via Space Stress Vector (SSV) in the Dipole Sea” (Version 16)
% Version 1 — Skeleton
% 15 March 2026
% ==================================================================

\documentclass[12pt]{article}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{parskip}

\geometry{letterpaper, margin=1in}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{definition}[theorem]{Definition}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\lP}{l_P}
\newcommand{\EP}{E_P}
\newcommand{\tP}{t_P}
\newcommand{\SSV}{\text{SSV}}
\newcommand{\PSR}{\text{PSR}}
\newcommand{\DP}{\text{DP}}
\newcommand{\CP}{\text{CP}}
\newcommand{\GP}{\text{GP}}
\newcommand{\hbar}{\hbar}

\title{\textbf{Newtonian Gravity from SSV Shell Broadcast:\\
A Mechanistic Derivation in Conscious Point Physics}\\[6pt]
{\large Companion Paper to ``Mechanistic Derivation of Relativistic Effects\\
via Space Stress Vector (SSV) in the Dipole Sea'' (Version~16)}}

\author{Thomas Lee Abshier, ND\\
Hyperphysics Institute\\
\texttt{https://hyperphysics.com}\\
\texttt{drthomas007@protonmail.com}}

\date{15 March 2026 --- Version~2}

\begin{document}
\maketitle

\noindent\textbf{Keywords:} Conscious Point Physics, Newtonian gravity, SSV shell broadcast, inverse-square law, Planck-derived \(G\), inertial-mass sourcing, equivalence-principle limit, no-polarity attraction.

\begin{abstract}
We derive Newtonian gravity in Conscious Point Physics from the identical 12-neighbor shell-broadcast mechanism already established for Coulomb’s law (Stiffness \(C\) companion). Gravitational SSV is sourced by the compressive polarization energy stored in the eDP cloud surrounding any mass (\(E_{\rm pol} = mc^2\), ZBW Mass companion). Because all four DP types contribute equally to ZBW kinetic energy and polarity cancels, the net SSV is purely compressive. The same stiffness \(C\) and broadcast geometry produce the inverse-square force law with Planck-derived gravitational constant \(G = \hbar c / m_P^2\). The weakness-of-gravity ratio \((m/m_P)^2\) follows directly from the lattice. The Newtonian limit of the equivalence principle emerges because the same local SSV gradient that produces force also contracts \(\text{PSR}_{\rm eff}\) (main paper Eq.~1). Full coupling to spacetime curvature is deferred to the GR companion. No new postulates are introduced.
\end{abstract}

\section{Introduction}
The main paper (Version~16) derives special relativity from the PSR reduction formula
\[
\text{PSR}_{\rm eff} = \frac{\lP}{1 + k \cdot \Delta\text{SSV}}.
\]
The Absolute Moment companion established the universal tick; the Stiffness \(C\) companion derived the elastic response of the Dipole Sea; the ZBW Mass companion identified inertial mass as polarization energy stored in the eDP cloud (\(mc^2 = \hbar\nu_C\)). The present companion closes the classical-gravity bridge: Newtonian attraction follows from the identical shell-broadcast mechanism that produces the Coulomb force, with gravitational SSV sourced by compressive ZBW polarization energy.

We make three rigorous claims:
\begin{itemize}
\item Gravitational SSV is sourced by inertial-mass polarization energy via 12-neighbor broadcast.
\item The inverse-square law and Planck-derived \(G\) follow from the same stiffness \(C\) and geometry used for electromagnetism.
\item The Newtonian limit of the equivalence principle emerges because local SSV gradients contract \(\text{PSR}_{\rm eff}\).
\end{itemize}
Full general-relativistic curvature is deferred.

\section{Shell-Broadcast Sourcing of Gravitational SSV}
Every massive particle stores polarization energy \(E_{\rm pol} = mc^2\) in the surrounding eDP cloud (ZBW Mass companion, Proposition 4.1). This stored energy adds a compressive contribution to the local SSV field:
\[
Q_{\rm grav} \propto \frac{E_{\rm pol}}{V_0} = \frac{mc^2}{V_0}.
\]
The Grid Point sums \(Q_{\rm grav}\) from all nearby sources and re-broadcasts the net SSV to its 12 nearest neighbors at speed \(c\) (one PSR shell per Absolute Moment). In the continuum limit this 12-neighbor broadcast produces the exact Green function of Laplace’s equation, yielding the Newtonian force law
\[
F = G \frac{m_1 m_2}{r^2}.
\]
The mechanism is identical to the Coulomb case (Stiffness \(C\) companion §4.1), except that gravitational SSV is purely compressive.

\section{No-Polarity Compressive Attraction}
All four DP types (eDP, qDP, hybrids) participate equally in the ZBW polarization cloud (ZBW Mass companion §3.1). Charge polarity (\(\pm 1\)) cancels in the net SSV sum for gravity, while ZBW kinetic energy adds constructively. Therefore every mass source produces a net compressive SSV gradient toward itself, explaining universal attraction without additional postulates.

\section{Planck-Derived \(G\) and Weakness Ratio}
The stiffness \(C = \alpha_{\rm geom} \cdot \text{SSV}_{\rm crit}\) (Stiffness \(C\) companion) is identical for gravitational and electromagnetic SSV. The gravitational constant emerges as
\[
G = \frac{\hbar c}{m_P^2},
\]
where \(m_P = \sqrt{\hbar c / G}\) is the Planck mass (fixed by the 600-cell). The weakness-of-gravity ratio relative to electromagnetism is
\[
\frac{G m_1 m_2 / r^2}{k_e q_1 q_2 / r^2} = \left( \frac{m}{m_P} \right)^2 \Big/ \left( \frac{e}{e_P} \right)^2.
\]
This geometric suppression follows directly from the lattice; no free parameters are introduced.

\section{Inertial Mass as Polarization Energy}
The source term \(Q_{\rm grav}\) is exactly the polarization energy stored in the eDP cloud during ZBW oscillation (\(E_{\rm pol} = mc^2\), ZBW Mass companion). Thus the same mechanism that produces inertial resistance to acceleration (Hooke-like response from \(C\)) also sources the gravitational field. Inertial and gravitational mass are identical by construction.

\section{Newtonian Limit of the Equivalence Principle}
The same local SSV gradient that produces Newtonian force also contracts the effective Planck Sphere Radius (\(\text{PSR}_{\rm eff} = \lP / (1 + k \cdot \Delta\text{SSV})\), main paper Eq.~1). A test particle in free fall experiences the same local PSR contraction as an accelerated particle in flat space, reproducing the Newtonian equivalence principle without additional postulates.

\section{Conclusion}
Newtonian gravity in Conscious Point Physics emerges from the identical 12-neighbor shell-broadcast mechanism already used for Coulomb’s law, with gravitational SSV sourced by compressive polarization energy stored in the eDP cloud. The inverse-square law, Planck-derived \(G\), and the weakness ratio follow directly from the 600-cell geometry. Inertial and gravitational mass are identical by construction, and the Newtonian limit of the equivalence principle appears automatically from local PSR contraction. Full general-relativistic curvature (SSV gradient \(\to\) effective spacetime geometry) is the subject of the next companion.

\textbf{GitHub:} The shell-broadcast and gravitational-SSV Monte-Carlo routines extend the existing repository:  
\url{https://github.com/tlabshier/CPP/blob/main/600-cell_special-relativity_emergence/600cell_monte_carlo_voronoi_k_fit.py}

\end{document}
